---
title: "Calendar of forthcoming publications"
date: "`r Sys.Date()`"
output:
  github_document:
  html_document:
    df_print: paged
    toc: yes
---

## Public health intelligence calendar	
	
### Aim	

To provide one list of public health data and statistics due to be published in the following two weeks
	
### Scope	

Public health data and statistics from Public Health England, NHS Digital, NHS England and other government departments in England 
	
Sources checked	"Statistics release calendar
"
	https://www.gov.uk/search/research-and-statistics
	Public Health England's key activity document (also available to local authorities via the Directors of Public Health bulletin)
	
### Frequency	

Published weekly on a Friday
	
Disclaimer	All content and dates included in this calendar are subject to short notice change and possible cancellation – changes to dates will be amended in the following week's scan.


```{r setup, inlcude = FALSE, echo = FALSE}

knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	include = FALSE
)
library(pacman)


p_load(myScrapers, tidytext, quanteda, tidyverse, rvest, openxlsx)

```


```{r page-links}

url <- paste0("https://www.gov.uk/search/research-and-statistics?content_store_document_type=upcoming_statistics&page=", 1:82)

links <- map(url, get_page_links) %>%
  enframe()


links <- links %>%
  unnest(cols = "value") %>%
  filter(str_detect(value, "government")) %>%
  mutate(urls = paste0("https://www.gov.uk", value)) %>%
  filter(!str_detect(value, "organisations|how-government-works|nationalarchives"))

#head(links, 100)


```


```{r page-titles}

get_link <- function(url) {
  
  out <- read_html(url) %>%
  html_nodes(".gem-c-document-list__item-link") %>%
  html_text()
  out
}

titles <- map(url, get_link) %>%
  enframe() %>%
  unnest(cols = "value")

links <- bind_cols(links, titles)

```

```{r page-description}

get_description <- function(url) {
  
  out <- read_html(url) %>%
  html_nodes(".gem-c-document-list__item-description") %>%
  html_text()
  out
}

descriptions <- map(url, get_description) %>%
  enframe() %>%
  unnest(cols = "value") 

```




```{r page-metadata}

get_metadata <- function(url) {
  
  out <- read_html(url) %>%
  html_nodes(".gem-c-document-list__item-metadata") %>%
  html_text()
  out
}

meta <- map(url, get_metadata) %>%
  enframe() %>%
  unnest(cols = "value") 

meta <- meta %>%
  separate(value, remove = TRUE, c("a", "Document type",  "b", "c", "Organisation", "d", "e", "Release Date", "f", "g", "State"), sep = "\\n") %>%
  select(-c(a, b, c, d, e, f, g)) %>%
  mutate(`Release Date` = str_remove(`Release Date`, "Release date: "),
         State = str_remove(State, "State: "), 
         Organisation = str_remove(Organisation, "Organisation: "), 
         `Document type` = str_remove(`Document type`, "Document type: "))

#meta

```

## Calendar

```{r final-calendar, include = TRUE, echo = FALSE}
table <- bind_cols(links, meta, descriptions)

table <- table %>%
  select(-contains("name"), title = value1, description = value1)

table <- table %>%
  select(-value)

table <- table %>%
  mutate(link = paste0("<a href =",  urls,  ">Link</a>")) %>%
  select(-urls)

table <- rename(table, title = description, description = value2)

table %>%
  openxlsx::write.xlsx(paste0("forthcoming_pubs", Sys.Date(), ".xlsx"))

table %>%
  DT::datatable(escape = FALSE, filter = "top", rownames = FALSE)
```

